The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

### 2021-03-03 README.Rmd
renamed all cv_grid_sf object names to blocks
replace all cv_grid arguments with blocks

```{r}
focal_vs_comp_ex <- growth_ex %>%
  create_focal_vs_comp(comp_dist, cv_grid_sf = blocks_ex, id = "ID")
focal_vs_comp_ex
```

@@

```{r}
focal_vs_comp_ex <- focal_vs_comp_ex %>%
  run_cv(comp_dist = comp_dist, cv_grid = blocks_ex)
```

>>>>

```{r}
focal_vs_comp_ex <- growth_ex %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_ex, id = "ID")
focal_vs_comp_ex
```

@@

```{r}
focal_vs_comp_ex <- focal_vs_comp_ex %>%
  run_cv(comp_dist = comp_dist, blocks = blocks_ex)
```

### 2021-03-03 paper/forestecology.Rmd
replace all cv_grid arguments with blocks

```{r scbi-spatial-cv}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  run_cv(comp_dist = comp_dist, cv_grid = blocks_scbi)
```
```{r}
model_rmse_cv <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
model_rmse_cv
```

>>>>

```{r scbi-spatial-cv}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  run_cv(comp_dist = comp_dist, blocks = blocks_scbi)
```
```{r}
model_rmse_cv <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
model_rmse_cv
```
